Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-10 paper/paper.tex
incorporating Igor's explanation

Considering prioritization, we classified warnings in two kinds,
reflecting their likelihood of manifesting a real bug. Warnings of the
kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks, but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is more likely to be valid as it it did
not raise exceptions during the execution of the application code,
but, it manifests discrepancy through violation of an assertion
declared in the test. In contrast, warnings in the ``\lo{}'' group are
more likely to be asssociated with invalid inputs. They reflect the
cases where the anomaly is observed during the execution of functions,
which are part of the application. We found that different engines often
check pre-conditions of those functions differently. It can happen,
for example, that one engine enforces a weaker pre-condition on a
function input compared to another engine and that is acceptable. For
instance, it is acceptable to pass values greater than \Fix{x} to
function \CodeIn{\Fix{WWW}} in \Fix{y} but not in \Fix{z}. In
those cases, the infrastructure would observe a discrepancy that is
more likely to be associated with an invalid input produced by the
fuzzer, \ie{}, it is likely to be a bug in the test code not the
engine (library or runtime) code. Although we did find real bugs from
``\lo{}'' warnings, the proportion was much lower compared to
``\hi{}'' warnings. Overall, only \Fix{12\%} of the reals bugs we
found with fuzzing originated from ``\lo{}'' warnings. \Fix{quickly
  explain why LO can still be a bug.}

@@

\begin{figure}[h]
\begin{tabular}{ll}
\veight{} & ``Unexpected end of input''\\
\jsc{} & ``Unexpected end of script''\\
\smonkey{} & ``Expected expression, got end of script''
\end{tabular}
\caption{\label{fig:err-messages}Example error messages associated
  with a \lo{} warning. In this case, the test passes in \chakra.}
\end{figure}

\Igor{
  Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
  casos reportados como LO tambem podem ser considerados como um true positive.
  Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
  se um teste falha antes da linha em que ha uma assercao, entao a falha
  ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
  possivel observar um caso de bug obtido em um bucket classificado como LO.
  Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
  posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
  maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
  de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
  lancar Offset is outside the bounds.

  Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
  Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
  correto seria usar um levantar um erro
}

@@

    Outputs:
    #### V8
    RangeError: Offset is outside the bounds of the DataView
    #### Chakra
    RangeError: DataView operation access beyond specified buffer length
    #### SpiderMonkey
    RangeError: invalid or out-of-range index
    #### JavaScriptCore
    RangeError: byteOffset cannot be negative
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}True positive example in LO warnings.}
\end{figure}

>>>>

Considering prioritization, we classified warnings in two kinds,
reflecting their likelihood of manifesting a real bug. Warnings of the
kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks, but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is more likely to be valid as it it did
not raise exceptions during the execution of the application code,
but, it manifests discrepancy through violation of an assertion
declared in the test. In contrast, warnings in the ``\lo{}'' group are
more likely to be asssociated with invalid inputs. They reflect the
cases where the anomaly is observed during the execution of functions,
which are part of the application. We found that different engines
often check pre-conditions of those functions differently. It can
happen, for example, that one engine enforces a weaker pre-condition
on a function input compared to another engine and that is
acceptable. For instance, it is acceptable to pass values greater than
\Fix{x} to function \CodeIn{\Fix{WWW}} in \Fix{y} but not in
\Fix{z}. In those cases, the infrastructure would observe a
discrepancy that is more likely to be associated with an invalid input
produced by the fuzzer, \ie{}, it is likely to be a bug in the test
code not the engine (library or runtime) code. It is worth noting that
``\lo'' warnings can be bug
revealing. Figure~\ref{fig:lo-truepositive} shows one of these
cases. In this example, the test instantiates an \CodeIn{ArrayBuffer}
object and stores an 8-bit integer at the 0 position. According to the
specification~\cite{ecmas262-getviewvalue}, a \CodeIn{RangeError}
exception should be thrown if a negative value is passed to the
function \CodeIn{ToIndex}, indirectly called by the test case. In this
case, however, the \chakra{} engine did not throw any exception, which
violates the spec. This bug was fixed by developers after our bug
report and is no longer present in the most recent release of
\chakra. Despite that counter-example, most bugs we found emerged from
``\hi{}'' warnings.

%% \Igor{
%%   Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
%%   casos reportados como LO tambem podem ser considerados como um true positive.
%%   Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
%%   se um teste falha antes da linha em que ha uma assercao, entao a falha
%%   ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
%%   possivel observar um caso de bug obtido em um bucket classificado como LO.
%%   Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
%%   posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
%%   maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
%%   de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
%%   lancar Offset is outside the bounds.

%%   Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
%%   Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
%%   correto seria usar um levantar um erro
%% }

@@

%% \begin{figure}[h]
%% \begin{tabular}{ll}
%% \veight{} & ``Unexpected end of input''\\
%% \jsc{} & ``Unexpected end of script''\\
%% \smonkey{} & ``Expected expression, got end of script''
%% \end{tabular}
%% \caption{\label{fig:err-messages}Example error messages associated
%%   with a \lo{} warning. In this case, the test passes in \chakra.}
%% \end{figure}

@@

Engines Messages (1:V8, 2:JavaScriptCore, 3:SpiderMonkey):
1. RangeError: Offset is outside the bounds of the DataView
2. RangeError: byteOffset cannot be negative
3. RangeError: invalid or out-of-range index
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}True positive example of LO
    warnings.}
\end{figure}
